---
title: "bio258_project_INM"
author: "Iris Mollhoff"
date: "2023-12-06"
output: html_document
---

# **Report** -- 2023.12.08
optimized code for processing, analyzing, and generating figures for a14 qPCR data from 96-well plate quant-studio-2 instrument.

# **R Code**
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Clear global enviornment
```{r}
rm(list = ls())
```

## for housekeeping gene
### load data for actin
```{r}
source("01_processing/loadfile.R")

rawcq_actin_acet1 <- loadfile("E:/Files/PhD Files 2 Iris Mollhoff/Git stuff/qPCR_analysis/data/","20210915_Tomato-Pst-A14_10hr_actin_acet1")
```
### clean, process, pull data for actin
```{r}
source("01_processing/processhkg.R")
list_hkg <- processhkg(rawcq_actin_acet1, "SlActin")

df_hkg <-list_hkg[[1]]
```
## for marker genes
### load data for 250 aand 270
```{r}
source("01_processing/loadfile.R")

rawcq_250_270 <- loadfile("E:/Files/PhD Files 2 Iris Mollhoff/Git stuff/qPCR_analysis/data/","20210915_Tomato-Pst-A14_10hr_250_270")
```

### Sl250
#### clean, process, pull data for Sl250
```{r}
source("01_processing/processhkg.R")
list_250 <- processhkg(rawcq_250_270, "Sl250")

df_250 <-list_hkg[[1]]
```
#### calculate delta Ct for sl250
```{r}
source("01_processing/deltact.R")

df2 <- deltact(df_250,df_hkg, "Sl250")
```
#### Statistics for sl250
```{r}
source("02_analysis/anova2x.R")

anova_treatment <- anova2x(df_250)
```
### figure for sl250
```{r}
source("03_figures/figure.R")

fig1a <- figure(df_250,"Sl 250-Desaturase (10hpi)")
```
### Save figure to file directory
```{r}
#source("03_figures/savefig.R")
#folder<-"E:/Files/PhD Files 2 Iris Mollhoff/Git stuff/qPCR_analysis/experiments/"
#filename<-"20231207_a14_acet1_6h_anovabonf"
#fig1a <- figure(fig1a,folder,filename)

#RETURNS: Error in figure(fig1a, folder, filename) : unused argument (filename)
```
```{r}
folder_location<-"E:/Files/PhD Files 2 Iris Mollhoff/Git stuff/qPCR_analysis/experiments/"
file_name<-"20231208_a14_acet1_10h_anovabonf" 
##change file name but keep directory the same

path <-paste(folder_location,file_name,".png",sep = "")
  
  ggsave(filename = path,
         device = "png",
         height = 4, width = 5)
  path
```


