---
title: "Untitled"
author: "Iris Mollhoff"
date: "2024-01-29"
output: html_document
---

# **Report** -- 2024.01.29
This r-markdown contains the code to reproducibly load qPCR data, process, perform statistical analysis, and generate figures. 
Raw data is sourced from the data directory. Functions are sourced from the 01_processing folder in the experiments directory.Final figures are saved ast .png files in the experiments directory.

## **Goals**
1. Check housekeeping genes have low variance. actin vs. VIN3
done
2. Determine if FLS3 and WAK1 espression in response to flgII-28 in WT plants is as expected.
done
3. Determine optimal time window for future WT vs delta-ACET1 comparison
done

# **R Code**
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Clear global enviornment
```{r}
rm(list = ls())
```
##Load required packages
```{r}
library(pcr)
library(tidyverse)
library(ggpubr)
library(readxl)
library(scales)
library(ggtext)
library(multcomp)
library(lsmeans)
library(rcompanion)
library(viridis)
library(ggprism)
library(FSA)
library(gtools)
library(gginnards)
library(multcompView)
library(ggtext)
library(scales)
library(rstatix)
library(pastecs)
library(car)
```

## load data
```{r}
source("01_processing/loadfile_csv.R")

datafolder <- "E:/Files/PhD Files 2 Iris Mollhoff/Git stuff/qPCR_analysis_flgII28/data/"

rawcq_a <- loadfile_csv(datafolder,"20240125_a83_ACET1_actin-FLS3-WAK1")
rawcq_w <- loadfile_csv(datafolder,"20240122_a83_WT_actin-vin3-fls3-wak1")
                      
key <- loadfile_csv(datafolder,"20221022_a83_samplekey")
```