---
title: "Untitled"
author: "Iris Mollhoff"
date: "2024-01-29"
output: html_document
---

# **Report** -- 2024.01.29
This r-markdown contains the code to reproducibly load qPCR data, process, perform statistical analysis, and generate figures. 
Raw data is sourced from the data directory. Functions are sourced from the 01_processing folder in the experiments directory.Final figures are saved ast .png files in the experiments directory.

## **Goals**
1. Check housekeeping genes have low variance. actin vs. VIN3
done
2. Determine if FLS3 and WAK1 espression in response to flgII-28 in WT plants is as expected.
done
3. Determine optimal time window for future WT vs delta-ACET1 comparison
done

# **R Code**
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Clear global enviornment
```{r}
rm(list = ls())
```
##Load required packages
```{r}
library(pcr)
library(tidyverse)
library(ggpubr)
library(readxl)
library(scales)
library(ggtext)
library(multcomp)
library(lsmeans)
library(rcompanion)
library(viridis)
library(ggprism)
library(FSA)
library(gtools)
library(gginnards)
library(multcompView)
library(ggtext)
library(scales)
library(rstatix)
library(pastecs)
library(car)
```

## load data
```{r}
source("01_processing/loadfile_csv.R")

datafolder <- "E:/Files/PhD Files 2 Iris Mollhoff/Git stuff/qPCR_analysis_flgII28/data/"

rawcq_a <- loadfile_csv(datafolder,"20240125_a83_ACET1_actin-FLS3-WAK1")
rawcq_w <- loadfile_csv(datafolder,"20240122_a83_WT_actin-vin3-fls3-wak1")
                      
key <- loadfile_csv(datafolder,"20221022_a83_samplekey")
```


## Process data
### clean data
```{r}
source("01_processing/cleandata1_384.R")
d_a <- cleandata1_384(rawcq_a, "Sample")
d_w  <- cleandata1_384(rawcq_w, "Sample")
```

### clean key
```{r}
source("01_processing/cleankey2.R")
k <- cleankey2(key,"sample")
```

###Combine data and key
```{r}
df_a <- right_join(k,d_a,by = c("Sample"))
df_w <- right_join(k,d_w,by = c("Sample"))
```

###Combine data from WT and ACET
```{r}
df <- bind_rows(df_a,df_w)
```

### calculate techrep
```{r}
source("01_processing/calctecrep1_384.R")

df1 <- calctecrep1_384(df)
```

### Pull actin (housekeeping gene)
```{r}
source("01_processing/pullhkg_384.R")

df_actin <- pullhkg_384(df1, "SlAct")
```

### calculate delta Ct and log delta ct--- for SlFLS3
```{r}
source("01_processing/deltact_384.R")

list_df2 <- deltact_384(df1,df_actin, "SlFLS3", c("Sample","genotype","treatment", "time", "rep"))
#returns list of tables (1)is delta cq or delta ct. (2) is the isolated marker gene

df1_marker <-list_df2[[2]] #the ct table for the marker of interest
df2_marker <-list_df2[[1]] #the delta-ct table
```

```{r}
#calculate average delta-Ct and 2^delta CT
df3_marker <- df2_marker %>% 
    dplyr::group_by(genotype,time,treatment) %>% 
    mutate(log_d_cq = 2^(-1*(d_cq)))
```
```{r}
df3_marker$genotype <- factor(df3_marker$genotype, levels=c("WT", "ACET1"))
```


## Data analysis
### Summary Statistics
```{r}
#source("02_analysis/anova2x.R")
#anova_treatment <- anova2x(df2)
```
```{r}
df3_marker %>%
  group_by(genotype, treatment, time) %>%
  get_summary_stats(d_cq, type = "mean_sd")
```
###Visualize data
```{r}
bxp <- ggboxplot(
  df3_marker, x = "time", y = "log_d_cq", 
  color = "genotype", palette = "jco",
  facet.by = "treatment", short.panel.labs = FALSE
  )
bxp
```
###check outliers
```{r}
df3_marker %>%
  group_by(genotype, treatment, time) %>%
  identify_outliers(log_d_cq)
```
**2024.01.09 result** - no outliers found in this dataset

###check normality assumption
```{r}
  #trim unused variables
  df4_marker<- df3_marker %>% 
    dplyr::select(!c(Target.x,marker_cq:hkg_cq)) %>% 
    ungroup() %>%
    relocate(Sample) %>% 
    na.omit()
```
```{r}
df4_marker %>%
  group_by(genotype, treatment, time) %>%
  shapiro_test(log_d_cq)
```
**2024.01.09 result** - samples that break normality assumption: WT-flg28-3h, ACET1-flg28-0h, ACET1-flg28-9h

###check qq-plot
```{r}
ggqqplot(df4_marker, "log_d_cq", ggtheme = theme_bw()) +
  facet_grid(genotype + treatment ~ time, labeller = "label_both")
```

###Run 3xANOVA test
```{r}
#test 3-way anova on  delta ct
res.aov <- anova_test(data = df4_marker, 
                        dv = d_cq, wid = rep,
                        within = c(genotype, treatment, time))
 res.aov
```
**RESULT 2024.01.29** found No 2-way effect. no 3-way effect. only sigle effect by genotype and time

```{r}
#test 3-way anova on antilog-transformed delta ct
res.aov.2 <- anova_test(data = df4_marker, 
                        dv = log_d_cq, wid = rep,
                        within = c(genotype, treatment, time))
 res.aov.2
```
**RESULT 2024.01.29** No single effect, no 2-way effect, and no 3-way effect was found

###Test simple 2-way interaction
```{r, eval=FALSE}
# Two-way ANOVA at each treatment
two.way <- df_trim %>%
  group_by(treatment) %>%
  anova_test(dv = d_cq, wid = rep, within = c(genotype, time))
two.way
```
```{r}
# Two-way ANOVA at each time
two.way1 <- df4_marker %>%
  group_by(time) %>%
  anova_test(dv = d_cq, wid = rep, within = c(genotype, treatment))
two.way1
```
```{r, eval=FALSE}
# Two-way ANOVA at each genotype
two.way2 <- df_trim %>%
  group_by(genotype) %>%
  anova_test(dv = d_cq, wid = rep, within = c(time, treatment))
two.way2
```
**RESULT 2024.01.29** did NOT find a simple 2-way interaction by genotype and treatment at any time.

```{r}
# Two-way ANOVA at each time using antilog-transformed data
two.way1.1 <- df4_marker %>%
  group_by(time) %>%
  anova_test(dv = log_d_cq, wid = rep, within = c(genotype, treatment))
two.way1.1
```
**RESULT 2024.01.29** did not find a simple 2-way interaction by genotype and treatment 

###Compute simple main effect
```{r, eval=FALSE}
# Effect of time at each genotype X treatment cells
time.effect <- df_trim %>%
  group_by(genotype, treatment) %>%
  anova_test(dv = d_cq, wid = rep, within = time)
time.effect
```
```{r}
# Effect of genotype at each treatment X time cells
gen.effect <- df4_marker %>%
  group_by( treatment, time) %>%
  anova_test(dv = d_cq, wid = rep, within = genotype )
gen.effect
```
**RESULT 2024.01.29** significant genotype effect only found with delta ct values (not log delta ct)
flg28-6h, mock-3h, mock-9h

```{r}
# Effect of genotype at each treatment X genotype cells
time.effect <- df4_marker %>%
  group_by(  treatment, genotype) %>%
  anova_test(dv = d_cq, wid = rep, within = time)
time.effect
```
**RESULT 2024.01.29** no time effect using delta ct values or log delta ct values

```{r}
# Effect of genotype at each treatment X time cells
trt.effect <- df4_marker %>%
  group_by(  genotype , time) %>%
  anova_test(dv = d_cq, wid = rep, within = treatment)
trt.effect
```
**RESULT 2024.01.29** no treatment effect

```{r}
#set up variable for automatically setting height of p-value bars
  p.val.ht <- max(df4_marker$log_d_cq)
```

###Compute simple simple comparisons
```{r}
#calculate pairwise comparison for genotype effect by t-test with bonferroni correction
  pwc1 <- df4_marker %>%
    group_by(treatment,time) %>%
    pairwise_t_test(
      log_d_cq ~ genotype, paired = TRUE,
      p.adjust.method = "bonferroni") %>%
    mutate(y.position = 1.1*p.val.ht)
pwc1
```
**RESULT 2024.01.29**  not significant for log delta ct data

```{r}
#calculate pairwise comparison for genotype effect by t-test with bonferroni correction
  pwc2 <- df4_marker %>%
    group_by(treatment,time) %>%
    pairwise_t_test(
      d_cq ~ genotype, paired = TRUE,
      p.adjust.method = "bonferroni") %>%
    mutate(y.position = .25*p.val.ht)
pwc2
```

**RESULT 2024.01.29** significant genotype effect only found with delta ct values:
flg28-6h, mock-3h, mock-9h



## Generate figures
###base Figure on log delta-cq compare by genotype
```{r}
bxp1 <- ggboxplot(
  df4_marker, x = "time", y = "log_d_cq", 
  color = "genotype", palette = "jco",
  facet.by = "treatment", short.panel.labs = FALSE,
  add = "jitter"
  )
bxp1
```
####p-value modification on figure for genotype effect from log delta cq
```{r}
# Visualization: box plots with p-values
pwc1 <- pwc1 %>% add_xy_position(x = "time")
pwc1.filtered <- pwc1 %>% 
  filter(time == "3"|time == "6"|time == "9")

bxp1 + 
  stat_pvalue_manual(pwc1.filtered, tip.length = 0) +
  labs(
    title = "Sl FLS",
    subtitle = get_test_label(res.aov.2, detailed = TRUE),
    caption = get_pwc_label(pwc1),
    x="Time (hrs)", y= "Relative Transcript Abundance / Sl Actin"
  )
```
#### Save figure 1 to file directory
```{r}
folder_location<-"E:/Files/PhD Files 2 Iris Mollhoff/Git stuff/qPCR_analysis_flgII28/experiments/"
file_name<-"20240129_a83_WT-ACET1_FLS3_genotype_y40_logdcq" 
##change file name but keep directory the same

path <-paste(folder_location,file_name,".png",sep = "")
  
  ggsave(filename = path,
         device = "png",
         height = 5, width = 5)
  path
```

####p-value modification on figure for genotype effect from  delta cq
```{r}
# Visualization: box plots with p-values
pwc2 <- pwc2 %>% add_x_position(x = "time") #used to by add_xy_position
pwc2.filtered <- pwc2 %>% 
  filter(time == "3"|time == "6"|time == "9")

bxp1 + 
  stat_pvalue_manual(pwc2, label="p.adj", tip.length = 0,bracket.shorten = 1.01 ) +
  labs(
    title = "Sl FLS",
    subtitle = get_test_label(res.aov, detailed = TRUE),
    caption = get_pwc_label(pwc1),
    x="Time (hrs)", y= "Relative Transcript Abundance / Sl Actin") +
  ylim(0,10)
```

#### Save figure 2 to file directory
```{r}
folder_location<-"E:/Files/PhD Files 2 Iris Mollhoff/Git stuff/qPCR_analysis_flgII28/experiments/"
file_name<-"20240129_a83_WT-ACET1_FLS3_genotype_y10_dcq" 
##change file name but keep directory the same

path <-paste(folder_location,file_name,".png",sep = "")
  
  ggsave(filename = path,
         device = "png",
         height = 5, width = 5)
  path
```




